Robust damped rank-reduction method for simultaneous denoising and reconstruction of 5D seismic data

### 2021-02-04 rdrr5d/paper.tex
2021年 2月 4日 星期四 10时31分49秒 CST

The following workflow presents our proposed robust damped rank-reduction algorithm for simultaneous denoising and reconstruction of 5D seismic data:

@@

\wen{For the first case,} we generate a 5D data model with the size of $100 \times 12 \times 12 \times 12 \times 12$, \wen{where}\dlo{which is composed of linear events.} $12 \times 12 \times 12 \times 12$ denotes the spatial size of the model. \wen{We conduct many experiments with this data}. In the first experiment, we randomly decimate $70\%$ of the traces and add a noise \dlo{variance of 0.3}\wen{of 0.3 variance} to examine the simultaneous denoising and reconstruction quality of both algorithms. The 3D figures in one common-midpoint gather \dlo{($Nx_1$ = 6, $Nx_2$ = 6)}\wen{($x$ = 6, $y$ = 6)} and one common offset gather \dlo{($x_1$ = 6, $x_2$ = 6)}\wen{($hx$ = 6, $hy$ = 6)} of the true, noisy, and decimated data are presented in Figures \ref{synth-clean-hxhy}\dlo{(a)}-\ref{synth-obs-hxhy}\dlo{(c)} and \ref{synth-clean-hxhy}\dlo{(a)}-\ref{synth-obs-hxhy}\dlo{(c)}, respectively.

The S/N\wen{s} of the noisy and observed data are extremely low with values of {$-$5.38 dB} and {$-$2.40 dB}, respectively. It is difficult to detect any coherent \dlo{valid}events in the observed noisy and incomplete data. To restore the useful signal, we use a rank {$K$ = 6} and a damped factor {$d$ = 2} for the DRR approach. Figures \ref{synth-drr-hxhy}\dlo{(d)} and \ref{synth-drr-xy}\dlo{(d)} show the results obtained using the DRR method. The simultaneously denoised and reconstructed data are satisfactory. Indeed, almost all signals are restored and the random noise has been perfectly reduced. However, the visual examination reveals some residual noise in the results. Using the proposed algorithm, with the same parameters used for DRR approach, we use a valid combination of cooling factor ${\beta = 3.3}$, rational transfer function coefficient ${e = 0.972}$, and window size ${T = 1}$. We run both methods using \dlo{ten}\wen{10} weighted POCS-like iterations. Figures \ref{synth-rdrr-hxhy}\dlo{(e)} and \ref{synth-rdrr-xy}\dlo{(e)} show the results obtained via the proposed RR approach. Compared with the DRR results, our method greatly removes the residual noise and recovers the useful signal. The output S/Ns for the DRR and the proposed approaches are {$15.55$} and {$21.89$ dB}, respectively. From the visual examination and the S/Ns comparison, we deduce that the restoration of the useful signal by the proposed approach is better than the DRR method.

\AtEndDocument{
	\begin{center}
		\begin{table}[h]
			\caption{Comparison of running time of the DRR and the proposed approach for different data sizes after \dlo{10}\wen{ten} iterations and a frequency band of $0-100$ Hz based on an Intel Core i7 7th Gen.}
			\begin{tabular}{c c c c c c} 
				\hline Test &$100\times8\times8\times8\times8$
				& $100\times10\times10\times10\times10$  & $100\times12\times12\times12\times12$ & \\ 
				\hline \dlo{DMSSA} \wen{DRR} (s) & 57.83 & 495.14 & 4419.36\\
				Proposed (s) & 48.64 & 469.69 & 4359.02 \\
				\hline
			\end{tabular} 
			\label{tbl:table1}
		\end{table}
	\end{center}
}
\wen{
	\AtEndDocument{
		\begin{center}
			\begin{table}[htb!]
				\caption{Comparison of S/N values among the ST, MA, STMA, RR, RR + ST, RR + MA, RR + damping factor (DRR), DRR + ST, RR + STMA, DRR + MA, and DRR + STMA (RDRR) for $0.3$ as noise variance and $70\%$ missing traces after \dlo{ten}\wen{10} iterations.}
				\begin{tabular}{c c c c c c} 
					\hline Approaches & S/N (dB) after 10 weighted {POCS-like} iterations & \\ 
					\hline ST& -1.77 & \\
					MA & 9.20 & \\
					STMA & 9.97 &\\
					RR & 11.83 &\\
					RR + ST & 11.83 &\\
					RR + MA &12.51&\\
					RR + damping factor (DRR) &15.55&\\
					RR + damping factor + ST & 15.55 &\\
					RR + STMA & 17.01 &\\
					RR + damping fator + MA & 21.17 &\\
					RR + damping factor + STMA (RDRR) & 21.89 &\\
					\hline
				\end{tabular} 
				\label{tbl:table2}
			\end{table}
		\end{center}
}}
\AtEndDocument{
%	\begin{figure}[htb!]
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/cmp_originalfinal}
%			\label{cmp_originalfinal}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/cmp_noisyfinal}
%			\label{cmp_noisyfinal}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/cmp_observedfinal}
%			\label{cmp_observedfinal}}\\	
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/cmp_drrokfinal}
%			\label{cmp_drrokfinal}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/cmp_proposedfinal}
%			\label{cmp_proposedfinal}}	
%		\caption{Common midpoint 3-D figures comparison ($x$ = 6, $y$ = 6) between \dlo{both}\wen{two} algorithms after \dlo{10}\wen{ten} iterations. (a) Clean data. (b) Noisy data with $ 0.3 $ as noise level. (c) Observed noisy and incomplete data with $70\%$ of missing traces. (d and e) Simultaneously denoised and reconstructed data using the DRR method and the proposed method, respectively.}
%		\label{cmp_originalfinal,cmp_noisyfinal,cmp_observedfinal,cmp_drrokfinal,cmp_proposedfinal}
%	\end{figure}%fig.1
\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-clean-hxhy}\label{synth-clean-hxhy}}
	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-noisy-hxhy}\label{synth-noisy-hxhy}}
	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-obs-hxhy}\label{synth-obs-hxhy}}\\
	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-drr-hxhy}\label{synth-drr-hxhy}}
	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-rdrr-hxhy}\label{synth-rdrr-hxhy}}
	\caption{Common-midpoint 3D figures comparison ($x$ = 6, $y$ = 6) between \dlo{both}\wen{two} algorithms after \dlo{ten}\wen{10} iterations. (a) Clean data. (b) Noisy data with $0.3$ as noise level. (c) Observed noisy and incomplete data with $70\%$ of missing traces. (d and e) Simultaneously denoised and reconstructed data using the DRR method and the proposed method, respectively.}
	\label{synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-drr-hxhy,synth-rdrr-hxhy}
\end{figure}%fig.1
%\begin{figure}[htb!]
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/offset_originalfinal}
%			\label{offset_originalfinal}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/offset_noisyfinal}
%			\label{offset_noisyfinal}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/offset_observedfinal}
%			\label{offset_observedfinal}}

%		\centering
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/offset_drrokfinal}
%			\label{offset_drrokfinal}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/offset_proposedfinal}
%			\label{offset_proposedfinal}}
%		\caption{Common offset gather 3-D figures comparison ($hx$ = 6, $hy$ = 6) between \dlo{both}\wen{two} algorithms after \dlo{10}\wen{ten} iterations. (a) True data. (b) Noisy data with $ 0.3 $ as noise level. (c) Observed noisy and incomplete data with $ 70\% $ of %missing traces. (d and e) Simultaneously denoised and reconstructed data using the DRR method and the proposed approach, respectively.}
%		\label{offset_originalfinal,offset_noisyfinal,offset_observedfinal,offset_drrokfinal,offset_proposedfinal}
%	\end{figure}%fig.2
\begin{figure}[htb!]
	\centering
	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-clean-xy}\label{synth-clean-xy}}
	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-noisy-xy}\label{synth-noisy-xy}}
	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-obs-xy}\label{synth-obs-xy}}\\
	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-drr-xy}\label{synth-drr-xy}}
	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-rdrr-xy}\label{synth-rdrr-xy}}
	\caption{Common-offset gather 3D figures comparison ($hx$ = 6, $hy$ = 6) between \dlo{both}\wen{two} algorithms after \dlo{ten}\wen{10} iterations. (a) True data. (b) Noisy data with $0.3$ as noise level. (c) Observed noisy and incomplete data with $70\%$ of missing traces. (d and e) Simultaneously denoised and reconstructed data using the DRR method and the proposed approach, respectively.}
	\label{synth-clean-xy,synth-noisy-xy,synth-obs-xy,synth-drr-xy,synth-rdrr-xy}
\end{figure}%fig.2
}
%\dlo{To make a good comparison based on visual examination, we plot the 2-D figures of each synthetic 5-D data aforementioned. The results in one common midpoint gather and one common offset gather are displayed in Figures \ref{3} and \ref{5}, respectively. Figures \ref{3}\dlo{(a)}\wen{a} and \ref{5}\dlo{(a)}\wen{a} denote the original data. Figures \ref{3}\dlo{(b)}\wen{b} and \ref{5}\dlo{(b)}\wen{b} show the noisy data. Figures \ref{3}\dlo{(c)}\wen{c} and \ref{5}\dlo{(c)}\wen{c} show the decimated data. Figures \ref{3}\dlo{(d)}\wen{d} and \ref{5}\dlo{(d)}\wen{d} display the simultaneously denoised and reconstructed data using the DRR algorithm. From this comparison, it is clear that the results obtained by our algorithm displayed in Figures \ref{3}\dlo{(e)}\wen{e} and \ref{5}\dlo{(e)}\wen{e} are still preferable than those of the DRR method.}
%\AtEndDocument{
%	\begin{figure}[htb!]
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2Dcmpclean7003}
%			\label{a}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DcmpNoisy7003}
%			\label{b}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DcmpObserved7003}
%			\label{Fiigure:c}}\\
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DcmpDRR7003}
%			\label{Fiigure:d}}
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DcmpProposed7003}
%			\label{Fiigure:e}}
%		\caption{Common midpoint 2-D figures comparison ($Nx_1$ = 6, $Nx_2$ = 6) after 10 iterations between both algorithms. (a) Clean data. (b) Noisy data with 0.3 as noise level. (c) Observed noisy and incomplete data with 70\% of missing traces. (d-e) Simultaneously denoised and reconstructed  data using the DRR method and the proposed approach, respectively.}
%		\label{3}
%	\end{figure}
%}
To see the difference more clearly, we display the rms error results obtained by subtracting the recovered data from the original data in \wen{Figure \ref{synth-drr-hxhy-e,synth-rdrr-hxhy-e,synth-drr-xy-e,synth-rdrr-xy-e}. Figures \ref{synth-drr-hxhy-e}\dlo{(a)} and \ref{synth-drr-xy-e}\dlo{(c)} correspond to the DRR approach with rms error values of $2.22\%$ and $2.64\%$ respectively in one common-midpoint and common-offset gather. Figure \ref{synth-rdrr-hxhy-e}\dlo{(b)} and \ref{synth-rdrr-xy}\dlo{(d)} is from the proposed algorithm with rms error values of $1.53\% $ and $1.48\% $ respectively in one common-midpoint and common-offset gathers.} From this comparison, it is \dlo{further} apparent that our approach performs better with fewer denoising and reconstruction errors and thus can provide a better simultaneously denoised and reconstructed improvement than the DRR algorithm. This comparison confirms the superiority of our approach in terms of accuracy. 
\AtEndDocument{
%	\begin{figure}[htb!]
%		\centering
%		\subfloat[]{\includegraphics[width=0.34\textwidth]{Figures/cmp_drrokerrfinal}
%			\label{cmp_drrokerrfinal}}
%		\subfloat[]{\includegraphics[width=0.34\textwidth]{Figures/cmp_proposederrfinal}
%			\label{cmp_proposederrfinal}}\\
%		\subfloat[]{\includegraphics[width=0.34\textwidth]{Figures/diff_offset_drrokfinal}
%			\label{diff_offset_drrokfinal}}
%		\subfloat[]{\includegraphics[width=0.34\textwidth]{Figures/diff_offset_proposedfinal}
%			\label{diff_offset_proposedfinal}}
%		\caption{Simultaneous denoising and reconstruction error \wen{3-D figures} comparison between \dlo{both}\wen{two} algorithms after \dlo{10}\wen{ten} iterations. (a and c) show the DRR approach with RMSE values of $ 2.22\% $ and $ 2.64\% $ in one common midpoint and one common offset gathers, respectively. (b and d) correspond to the proposed approach with RMSE values of $ 1.53\% $ and $ 1.48\% $ in one common midpoint and one common offset gathers, respectively.}
%		\label{cmp_drrokerrfinal,cmp_proposederrfinal,diff_offset_drrokfinal,diff_offset_proposedfinal}
%	\end{figure}%fig.3
\begin{figure}[htb!]
		\centering
	        \subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-drr-hxhy-e}\label{synth-drr-hxhy-e}}
	        \subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-rdrr-hxhy-e}\label{synth-rdrr-hxhy-e}}\\
	        \subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-drr-xy-e}\label{synth-drr-xy-e}}
	        \subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-rdrr-xy-e}\label{synth-rdrr-xy-e}}
		\caption{Simultaneous denoising and reconstruction error \wen{3D figures} comparison between \dlo{both}\wen{two} algorithms after \dlo{10}\wen{ten} iterations. (a and c) show the DRR approach with rms error values of $2.22\%$ and $2.64\%$ in one common-midpoint and one common-offset gather, respectively. (b and d) correspond to the proposed approach with rms error values of $1.53\%$ and $1.48\%$ in one common-midpoint and one common-offset gather, respectively.}
		\label{synth-drr-hxhy-e,synth-rdrr-hxhy-e,synth-drr-xy-e,synth-rdrr-xy-e}
	\end{figure}%fig.3
}
%\begin{figure}[htb!] 
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2Doffsetclean7003}
%			\label{a}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DoffsetNoisy7003}
%			\label{b}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DoffsetObserved7003}
%			\label{Fiigure:c}}\\
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DoffsetDRR7003}
%			\label{Fiigure:d}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DoffsetProposed7003}
%			\label{Fiigure:e}}	
%		\caption{Common offset 2-D figures comparison ($x_1$ = 6, $x_2$ = 6) after 10 iterations between both algorithms. (a) Clean data. (b) Noisy data with 0.3 as noise variance. (c) Observed noisy and incomplete data with 70\% of missing traces. (d-e) Simultaneously denoised and reconstructed data using both methods, respectively.}
%		\label{5}
%	\end{figure}
%	\begin{figure}[htb!]
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DRMSEoffsetDRR7003}
%			\label{a}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/2DRMSEoffsetProposed7003}
%			\label{b}}
%		\caption{Simultaneous reconstruction and denoising errors comparison in common offset ($x_1$ = 6, $x_2$ = 6) after 10 iterations between both algorithms. (a) shows the DRR approach with an RMSE of 2.64\%. (b) shows the proposed approach with an RMSE of 1.48\%.}

>>>>

The following workflow presents our proposed RDRR algorithm for simultaneous denoising and reconstruction of 5D seismic data:

@@

\wen{For the first case,} we generate a 5D data model with the size of $100 \times 12 \times 12 \times 12 \times 12$, \wen{where}\dlo{which is composed of linear events.} $12 \times 12 \times 12 \times 12$ denotes the spatial size of the model. \wen{We conduct many experiments with this data}. In the first experiment, we randomly decimate $70\%$ of the traces and add a noise \dlo{variance of 0.3}\wen{of 0.3 variance} to examine the simultaneous denoising and reconstruction quality of both algorithms. The 3D figures in one common-midpoint gather \dlo{($Nx_1$ = 6, $Nx_2$ = 6)}\wen{($x$ = 6, $y$ = 6)} and one common-offset gather \dlo{($x_1$ = 6, $x_2$ = 6)}\wen{($hx$ = 6, $hy$ = 6)} of the true, noisy, and decimated data are presented in Figures \ref{fig:synth-clean-hxhy}\dlo{(a)}-\ref{fig:synth-obs-hxhy}\dlo{(c)} and \ref{fig:synth-clean-hxhy}\dlo{(a)}-\ref{fig:synth-obs-hxhy}\dlo{(c)}, respectively.

The S/N\wen{s} of the noisy and observed data are extremely low with values of {$-$5.38 dB} and {$-$2.40 dB}, respectively. It is difficult to detect any coherent \dlo{valid}events in the observed noisy and incomplete data. To restore the useful signal, we use a rank {$K$ = 6} and a damped factor {$d$ = 2} for the DRR approach. Figures \ref{fig:synth-drr-hxhy}\dlo{(d)} and \ref{fig:synth-drr-xy}\dlo{(d)} show the results obtained using the DRR method. The simultaneously denoised and reconstructed data are satisfactory. Indeed, almost all signals are restored and the random noise has been perfectly reduced. However, the visual examination reveals some residual noise in the results. Using the proposed algorithm, with the same parameters used for DRR approach, we use a valid combination of cooling factor ${\beta = 3.3}$, rational transfer function coefficient ${e = 0.972}$, and window size ${T = 1}$. We run both methods using \dlo{ten}\wen{10} weighted POCS-like iterations. Figures \ref{fig:synth-rdrr-hxhy}\dlo{(e)} and \ref{fig:synth-rdrr-xy}\dlo{(e)} show the results obtained via the proposed RR approach. Compared with the DRR results, our method greatly removes the residual noise and recovers the useful signal. The output S/Ns for the DRR and the proposed approaches are {$15.55$} and {$21.89$ dB}, respectively. From the visual examination and the S/Ns comparison, we deduce that the restoration of the useful signal by the proposed approach is better than the DRR method.

\AtEndDocument{
	\begin{center}
		\begin{table}[h]
			\caption{Comparison of running time of the DRR and the proposed approach for different data sizes after \dlo{10}\wen{ten} iterations and a frequency band of $0-100$ Hz based on an Intel Core i7 7th Gen.}
			\begin{tabular}{c c c c c c} 
				\hline Test &$100\times8\times8\times8\times8$
				& $100\times10\times10\times10\times10$  & $100\times12\times12\times12\times12$ & \\ 
				\hline \dlo{DMSSA} \wen{DRR} (s) & 57.83 & 495.14 & 4419.36\\
				Proposed (s) & 48.64 & 469.69 & 4359.02 \\
				\hline
			\end{tabular} 
			\label{tbl:table1}
		\end{table}
	\end{center}
}
\wen{
	\AtEndDocument{
		\begin{center}
			\begin{table}[htb!]
				\caption{Comparison of S/N values among the ST, MA, STMA, RR, RR + ST, RR + MA, RR + damping factor (DRR), DRR + ST, RR + STMA, DRR + MA, and DRR + STMA (RDRR) for $0.3$ as noise variance and $70\%$ missing traces after \dlo{ten}\wen{10} iterations.}
				\begin{tabular}{c c c c c c} 
					\hline Approaches & S/N (dB) after 10 weighted {POCS-like} iterations & \\ 
					\hline ST& -1.77 & \\
					MA & 9.20 & \\
					STMA & 9.97 &\\
					RR & 11.83 &\\
					RR + ST & 11.83 &\\
					RR + MA &12.51&\\
					RR + damping factor (DRR) &15.55&\\
					RR + damping factor + ST & 15.55 &\\
					RR + STMA & 17.01 &\\
					RR + damping fator + MA & 21.17 &\\
					RR + damping factor + STMA (RDRR) & 21.89 &\\
					\hline
				\end{tabular} 
				\label{tbl:table2}
			\end{table}
		\end{center}
}}
%\AtEndDocument{
%	\begin{figure}[htb!]
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/cmp_originalfinal}
%			\label{Figure:cmp_originalfinal}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/cmp_noisyfinal}
%			\label{Figure:cmp_noisyfinal}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/cmp_observedfinal}
%			\label{Figure:cmp_observedfinal}}\\	
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/cmp_drrokfinal}
%			\label{Figure:cmp_drrokfinal}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/cmp_proposedfinal}
%			\label{Figure:cmp_proposedfinal}}	
%		\caption{Common midpoint 3-D figures comparison ($x$ = 6, $y$ = 6) between \dlo{both}\wen{two} algorithms after \dlo{10}\wen{ten} iterations. (a) Clean data. (b) Noisy data with $ 0.3 $ as noise level. (c) Observed noisy and incomplete data with $70\%$ of missing traces. (d and e) Simultaneously denoised and reconstructed data using the DRR method and the proposed method, respectively.}
%		\label{Figure:cmp_originalfinal,cmp_noisyfinal,cmp_observedfinal,cmp_drrokfinal,cmp_proposedfinal}
%	\end{figure}%fig.1

\inputdir{synth_Linear_NV03_MT70}
\multiplot{5}{synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-drr-hxhy,synth-rdrr-hxhy}{width=0.3\textwidth}{Common-midpoint 3D figures comparison ($x$ = 6, $y$ = 6) between \dlo{both}\wen{two} algorithms after \dlo{ten}\wen{10} iterations. (a) Clean data. (b) Noisy data with $0.3$ as noise level. (c) Observed noisy and incomplete data with $70\%$ of missing traces. (d and e) Simultaneously denoised and reconstructed data using the DRR method and the proposed method, respectively.}

%\begin{figure}[htb!]
%	\centering
%	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-clean-hxhy}\label{Figure:synth-clean-hxhy}}
%	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-noisy-hxhy}\label{Figure:synth-noisy-hxhy}}
%	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-obs-hxhy}\label{Figure:synth-obs-hxhy}}\\
%	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-drr-hxhy}\label{Figure:synth-drr-hxhy}}
%	\subfloat[]{\includegraphics[width=0.35\textwidth]{synth_Linear_NV03_MT70/Fig/synth-rdrr-hxhy}\label{Figure:synth-rdrr-hxhy}}
%	\caption{Common-midpoint 3D figures comparison ($x$ = 6, $y$ = 6) between \dlo{both}\wen{two} algorithms after \dlo{ten}\wen{10} iterations. (a) Clean data. (b) Noisy data with $0.3$ as noise level. (c) Observed noisy and incomplete data with $70\%$ of missing traces. (d %and e) Simultaneously denoised and reconstructed data using the DRR method and the proposed method, respectively.}
%	\label{Figure:synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-drr-hxhy,synth-rdrr-hxhy}
%\end{figure}%fig.1
%\begin{figure}[htb!]
%		\centering
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/offset_originalfinal}
%			\label{Figure:offset_originalfinal}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/offset_noisyfinal}
%			\label{Figure:offset_noisyfinal}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/offset_observedfinal}
%			\label{Figure:offset_observedfinal}}

%		\centering
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/offset_drrokfinal}
%			\label{Figure:offset_drrokfinal}}
%		\subfloat[]{\includegraphics[width=0.3\textwidth]{Figures/offset_proposedfinal}
%			\label{Figure:offset_proposedfinal}}
%		\caption{Common offset gather 3-D figures comparison ($hx$ = 6, $hy$ = 6) between \dlo{both}\wen{two} algorithms after \dlo{10}\wen{ten} iterations. (a) True data. (b) Noisy data with $ 0.3 $ as noise level. (c) Observed noisy and incomplete data with $ 70\% $ of %missing traces. (d and e) Simultaneously denoised and reconstructed data using the DRR method and the proposed approach, respectively.}
%		\label{Figure:offset_originalfinal,offset_noisyfinal,offset_observedfinal,offset_drrokfinal,offset_proposedfinal}
%	\end{figure}%fig.2

\inputdir{synth_Linear_NV03_MT70}
\multiplot{5}{synth-clean-xy,synth-noisy-xy,synth-obs-xy,synth-drr-xy,synth-rdrr-xy}{width=0.3\textwidth}{Common-offset gather 3D figures comparison ($hx$ = 6, $hy$ = 6) between \dlo{both}\wen{two} algorithms after \dlo{ten}\wen{10} iterations. (a) True data. (b) Noisy data with $0.3$ as noise level. (c) Observed noisy and incomplete data with $70\%$ of missing traces. (d and e) Simultaneously denoised and reconstructed data using the DRR method and the proposed approach, respectively.}

To see the difference more clearly, we display the rms error results obtained by subtracting the recovered data from the original data in \wen{Figure \ref{fig:synth-drr-hxhy-e,synth-rdrr-hxhy-e,synth-drr-xy-e,synth-rdrr-xy-e}. Figures \ref{fig:synth-drr-hxhy-e}\dlo{(a)} and \ref{fig:synth-drr-xy-e}\dlo{(c)} correspond to the DRR approach with rms error values of $2.22\%$ and $2.64\%$ respectively in one common-midpoint and common-offset gather. Figure \ref{fig:synth-rdrr-hxhy-e}\dlo{(b)} and \ref{fig:synth-rdrr-xy}\dlo{(d)} is from the proposed algorithm with rms error values of $1.53\% $ and $1.48\% $ respectively in one common-midpoint and common-offset gathers.} From this comparison, it is \dlo{further} apparent that our approach performs better with fewer denoising and reconstruction errors and thus can provide a better simultaneously denoised and reconstructed improvement than the DRR algorithm. This comparison confirms the superiority of our approach in terms of accuracy.

\inputdir{synth_Linear_NV03_MT70}
\multiplot{4}{synth-drr-hxhy-e,synth-rdrr-hxhy-e,synth-drr-xy-e,synth-rdrr-xy-e}{width=0.35\textwidth}{Simultaneous denoising and reconstruction error \wen{3D figures} comparison between \dlo{both}\wen{two} algorithms after \dlo{wen}\wen{10} iterations. (a and c) show the DRR approach with rms error values of $2.22\%$ and $2.64\%$ in one common-midpoint and one common-offset gather, respectively. (b and d) correspond to the proposed approach with rms error values of $1.53\%$ and $1.48\%$ in one common-midpoint and one common-offset gather, respectively.}

\wen{Moreover,} we conduct a comparison between the amplitude of each corresponding \dlo{5-D}data \wen{plotted in Figure \ref{fig:synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-drr-hxhy,synth-rdrr-hxhy}} to highlight more distinctly the differences. Figure \dlo{\ref{fig:7}}\wen{\ref{fig:synth-ss}} displays a comparison between each amplitude. The green, yellow and black lines are, respectively, from the original, noisy, and observed data. The amplitude of the observed data cannot be detected in this figure due to the influence \dlo{of the percentage}of missing traces. The blue and red lines correspond to the DRR approach and proposed approach, respectively. Clearly shown in Figure \dlo{\ref{fig:7}}\wen{\ref{fig:synth-ss}}, the blue and red lines are very regular in most areas. However, we find that the green and red lines are \dlo{too much close} \wen{much closer} to each other. This comparison further demonstrates the high accuracy of the proposed algorithm.

\inputdir{synth_Linear_NV03_MT70}
\plot{synth-ss}{width=0.8\columnwidth}{Comparison of a single trace amplitude of each \dlo{5-D synthetic} data \wen{shown in Figure \ref{fig:synth-clean-hxhy,synth-noisy-hxhy,synth-obs-hxhy,synth-drr-hxhy,synth-rdrr-hxhy}}. The green line is from the clean data. The yellow line denotes the noisy data. The amplitude of the observed data denoted by the black line is zero and thus cannot be seen from the figure. The blue line corresponds to the DRR method. The red line corresponds to the proposed method. The proposed method can provide a good amplitude very close to the clean compared to the DRR method.}

\dlo{We further compare the performance of the DRR method and our approach from another aspect using the amplitude \dlo{and frequency-space (f-x)} spectra. According to the amplitude spectrum comparison displayed in Figure \dlo{\ref{fig:8}}\wen{\ref{fig:5}}, we deduce that both approaches can recover the signal. However, there is a remarkable difference in the amplitude in favor of our algorithm. It can be explained by the fact that DRR approach suppresses the residual noise at the entire frequency band to a relatively weak degree whereas our approach removes the residual noise sufficiently. That is why the amplitude spectrum of the proposed approach shown in Figure \dlo{\ref{Figure:8}(e)} \ref{Figure:5}(e) is perfect and very similar to that of the true data shown in Figure \dlo{\ref{Figure:8}(a)} \wen{\ref{Figure:5}(a)}. This analysis demonstrates one more time the better performance of the proposed algorithm compared to the DRR method. \wen{Therefore, we deduce that the proposed method can obtain successful results even though the observed noisy and incomplete data have very low amplitudes as shown in Figures \ref{Figure:5}(c)} \dlo{\ref{Figure:8}(c)}.}

Moreover, we conduct several numerical tests to compare the performances of both algorithms. The key idea of these experiments is to provide a practical guideline by quantifying the performance of both methods. They are implemented in terms of iterations number, \dlo{the} percentage of missing data, and \dlo{the}noise levels. Using the same observed noisy and incomplete 5D synthetic data corrupted by a noise level of $0.3$ and $70\%$ of missing traces, we \dlo{first} highlight the behavior of each method in terms of S/N \dlo{and RMSE}to the iteration numbers. \dlo{Figures \ref{Figure:11}(a) and \ref{fig:11}(b) show the S/N and rms error diagrams respectively, for}\wen{Figure \ref{fig:SNR_with_iterations} shows} the S/N \wen{values} for the iteration numbers \dlo{ranged}\wen{ranging} from $5$ to $30$. The blue and red lines indicate the S/N diagrams of the DRR method and the proposed approach, respectively. As shown on the figure\dlo{these figures}, it is visible that the proposed method surpasses the DRR method in terms of S/N\dlo{and RMSE}. \dlo{In both cases,}\wen{From this comparison, we find that} when the iteration number becomes large (approximately $25$), the S/N \wen{values} tends to decrease slightly.\dlo{Thus, the RMSE increases slowly.} We can therefore deduce from this analysis that both approaches behave the same way even though the proposed method is still better than the DRR method. From this comparison, which greatly highlights the accuracy of both methods concerning the iteration numbers, we can intuitively know the performance of each framework in terms of S/N \dlo{and RMSE}as the iteration number increase\wen{s}. 
\wen{From this figure, the best result from the proposed approach is at 15 iterations, whereas the best result from DRR is at 20 iterations. We find that the proposed method could save \old{$\frac{1}{4}$}\wen{25\%} of the computation\dlo{s} time, and \dlo{ten}\wen{10} \dlo{weight}\wen{weighted} POCS-like iterations can be used for the proposed method. Therefore, all examples in this paper are conducted with \dlo{ten}\wen{10} iterations.}

\inputdir{./}
\plot{SNR_with_iterations}{width=0.5\columnwidth}{Comparison of S/N diagrams regarding the iteration numbers. The blue and red lines correspond to the DRR and the proposed approaches, respectively. The performance of the proposed method is better than that of the DRR method as the iteration number increases. We decimated $70\%$ of traces and added a noise level of $0.3$ for this test.}
